Ecuador plant species IUCN data

### 2022-10-31 code/L0/L0_Ecuador_plants_IUCN.Rmd
add summary information using DataExplorer and summarytools packages

# Install and load required packages
```{r}
for (package in c("httr", "jsonlite", "rredlist", "dplyr", "mde")) {
  if (!require(package, character.only=T, quietly=T)) {
    install.packages(package)
    library(package, character.only=T)
  }
}
```
# Set up token and api url
```{r}
## Token for accessing IUCN data through their API
## User must obtain a token (https://apiv3.iucnredlist.org/api/v3/token) before using the 'rredlist package'.
token <- 'f632af67ee5eef8446a8cb0ca394e1f1cb369ca5eab626edc4ea46e5698deb25'
api_url <- 'https://apiv3.iucnredlist.org/api/v3/'

>>>>

# Install and load required packages
```{r}
library(httr)
library(jsonlite)
library(rredlist)
library(dplyr)
library(mde)
library(DataExplorer)
library(summarytools)
```

# Set up token and api url
```{r}
## Token for accessing IUCN data through their API
## User must obtain a token (https://apiv3.iucnredlist.org/api/v3/token) before using the 'rredlist package'.
token <- 'f632af67ee5eef8446a8cb0ca394e1f1cb369ca5eab626edc4ea46e5698deb25'
api_url <- 'https://apiv3.iucnredlist.org/api/v3/'
